Classless Java

### 2015-09-20 paper/sections/Overview.tex
shorter example in overview

\lstinputlisting[linerange=33-45]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT

@@

\lstinputlisting[linerange=50-77]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT_OF

>>>>

\lstinputlisting[linerange=6-10]{../UseMixinLombok/src/overview/TestPoint.java} % APPLY:linerange=POINT

@@

\lstinputlisting[linerange=15-27]{../UseMixinLombok/src/overview/TestPoint.java} % APPLY:linerange=POINT_OF
